---
title: "Homework 2"
author: "Shubham Bhargava"
date: "2024-02-11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
News_Website_Dataset <- read_excel("News Website Dataset.xlsx")
#View(News_Website_Dataset)

# correlation  and coefficient B/W Total_revenue and Total Sessions
correlation_coefficient2 <- cor(News_Website_Dataset$Total_revenue, News_Website_Dataset$Total_Sessions)
print(correlation_coefficient2)

plot(News_Website_Dataset$Total_Sessions, News_Website_Dataset$Total_revenue,
     xlab = "Total Sessions", ylab = "Total Revenue",
     main = "Scatter Plot of Total Revenue vs. Total Sessions")

abline(lm(News_Website_Dataset$Total_revenue ~ News_Website_Dataset$Total_Sessions), col = "green")

```
```{r}

correlation_coefficient <- cor(News_Website_Dataset$Total_revenue, News_Website_Dataset$Avg_Session_Duration)

plot(News_Website_Dataset$Avg_Session_Duration, News_Website_Dataset$Total_revenue,
     xlab = "Average Session Duration", ylab = "Total Revenue",
     main = "Scatter Plot of Total Revenue vs. Avg Session Duration")

abline(lm(News_Website_Dataset$Total_revenue ~ News_Website_Dataset$Avg_Session_Duration), col = "purple")

print(paste("Correlation Coefficient between Total Revenue and Avg Session Duration:", correlation_coefficient))

```

## Homework 2


<b>1.  Bivariate Analysis:</b>
<p><b>Question :</b> What differences exist in total revenue between various traffic sources?</p>

<p><b>Visualization:</b>  Box plot showing Total Revenue by Traffic Source</p>

```{r}
library(ggplot2)
ggplot(News_Website_Dataset, aes(x = Traffic_Source, y = Total_revenue, fill = Traffic_Source)) +
  geom_boxplot() +
  labs(title = "Total Revenue by Traffic Source",
       x = "Traffic Source",
       y = "Total Revenue")
```
<p>With certain traffic sources having larger median incomes than others, the box plot illustrates differences in overall revenue across various traffic sources.</p>

<b>2. Univariate Analysis:</b>
<p><b>Question :</b>  How is the overall revenue divided up?</p>

<p><b>Visualization:</b> Histogram showing Total Revenue</p>
```{r}
library(ggplot2)
hist(News_Website_Dataset$Total_revenue, 
     main = "Distribution of Total Revenue",
     xlab = "Total Revenue",
     ylab = "Frequency",
     col = "purple",
     border = "yellow")
```
<p>The total income distribution is displayed in the histogram. This indicates that income is dispersed to the right and resides primarily in the lower ranges. Small gains are deemed to be excessive.</p>

<b>3.  Multivariate Analysis:</b>
<p><b>Question :</b>What differences exist in overall income between various device categories and times of day?</p>

<p><b>Visualization:</b>  Line plot Showing Total Revenue by Time of Day, color by Device Category</p>

```{r}
library(ggplot2)
ggplot(News_Website_Dataset, aes(x = Time_of_Day, y = Total_revenue, color = Device_Category)) +  geom_line(size = 2.5) +
  labs(title = "Total Revenue by Time of Day (Colored by Device Category)",
       x = "Time of Day",
       y = "Total Revenue")
```
<p>With a distinct device category represented by each line, the line plot shows how total revenue changes during the day. Based on device usage and time of day, it aids in identifying revenue trends.</p>